{[}Add centre name and address{]}

\section{PATIENT INFORMATION SHEET}\label{patient-information-sheet}

This centre has implemented a trauma data bank. Before your data can be
included in this data bank the purpose of the data collection must be
explained to you, and you must be given the chance to ask questions.
Please read carefully the information provided here. If you agree to
participate, please sign the informed consent form. You will be given a
copy of this document to take home with you.

\textbf{Title:}

Principal Investigator(s): {[}Add investigator name{]}

\textbf{PURPOSE}

We are currently collecting data in this hospital to be included in an
institutional trauma data bank. The purpose of this data bank is to
provide quality data, which will be used for research that aims to
improve care and outcome of trauma patients. We ask you to participate
in this data bank because you present to this hospital after having an
injury.

\textbf{STUDY PROCEDURES AND VISIT SCHEDULE}

If you agree to participate, we will:

\begin{itemize}
\item
  Store health data registered in your hospital record and vital signs
  recordings from the emergency department
\item
  Contact you in person or by telephone for follow ups to obtain
  information about your health status at the following times:

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    On arrival at the emergency department
  \item
    On hospital discharge
  \item
    24 hours after discharge
  \item
    30 days after discharge
  \item
    6 months after discharge
  \item
    12 months after discharge
  \end{itemize}
\end{itemize}

When you arrived at the hospital, we recorded some basic parameters such
as your age, gender, and how you were injured. We also recorded health
data such as blood pressure, heart rate, and body temperature. If you
want complete information regarding all the parameters that were
recorded, please do not hesitate to ask, and we will be happy to inform
you. Should you wish that your data is deleted from data bank at this
hospital, please contact us using the contact information provided
below. The data bank may be used for research that can be published as
scientific articles; however, it will not be possible to identify you by
reading any article that may result from this data bank. Further, data
from this project will be combined with data from other hospitals that
use the same system and shared for other researchers and individuals to
use, but it will not be possible to identify you using that data.

\textbf{WITHDRAWAL FROM STUDY}

Participation in this data bank is completely voluntary. Even if you
agree to participate now you are free to withdraw at any time without
giving any reason for doing so. Withdrawing will not affect your
ordinary treatment or the care given to you. To withdraw contact any of
the contact persons using the contact information provided. Note that we
can only delete data from the data bank in this hospital. We cannot
delete data once it has been de-identified because we will not be able
to tell from whom the data came.

\textbf{POSSIBLE RISKS, DISCOMFORTS AND INCONVENIENCES}

We have not been able to identify any major risks associated with
participating in this study. Should there be any inconveniences you are
free to withdraw at that point, or at any time using the contact
information provided.

\textbf{POTENTIAL BENEFITS}

The data bank will be used for research and quality improvement that may
help to improve the care of injured patients. Although this project will
not affect the care you are given in this hospital at this time, your
participation will contribute to medical knowledge, and may improve care
for others that are injured.

\textbf{SUBJECT'S RIGHTS}

Your participation in this study is entirely voluntary. Your questions
will be answered clearly and to your satisfaction. In the event of any
new information becoming available that may be relevant to your
willingness to continue in this study, you will be informed in a timely
manner by the Principal Investigator or his/her representative.

\textbf{CONFIDENTIALITY OF STUDY AND MEDICAL RECORDS}

The results of this research may be published as a scientific article;
however, it will not be possible to identify you by reading any article
that may result from this work. Further, data from this project will be
combined with data from other hospitals that use the same system and
shared for other researchers and individuals to use, but it will not be
possible to identify you using that data.

Also, Regulatory Agencies, Institution Review Board and Ministry of
Health will be granted direct access to your original medical records to
check study procedures and data, without making any of your information
public. By signing the Informed Consent Form attached, you are
authorizing such access to your study and medical records.

\textbf{COSTS OF PARTICIPATION}

No charge will be levied on you if you take part in this project. You
will not receive any compensation for participating in this project.

\textbf{RESEARCH RELATED INJURY AND COMPENSATION}

Due to the observational nature of this project, it is unlikely to cause
any research related injury. The hospital will provide medical care for
any problems that may arise during this study.

\textbf{WHO TO CONTACT IF YOU HAVE QUESTIONS?}

If you have questions regarding this project and your rights, or in the
case of any injuries sustained during this project, you may contact the
Principal Investigator:

{[}Add study contact information{]}

\section{CONSENT FORM}\label{consent-form}

\textbf{Protocol Title:} Institutional Trauma Data Bank

\textbf{Subject's Particulars}

Name:

NRIC/PNR/SSN No.:

Address:

Date of birth \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ dd/mm/yyyy

Phone No:

Phone number(s) to your relatives or friends that you agree we may
contact if you do not answer your phone:

\begin{quote}
Part I- to be filled by patient
\end{quote}

I, \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (Pt ID
No.\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_) Agree / do not agree to
participate in the project as described and, on the terms detailed in
the Patient Information Sheet. The nature of my participation in the
proposed project has been explained to me in
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ by Dr/Mr/Ms
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_. I have fully discussed and
understood the purpose and procedures of this project. I have been given
the Patient Information Sheet and the opportunity to ask questions about
this project and have received satisfactory answers and information. I
understand that my participation is voluntary and that I am free to
withdraw at any time, without giving any reasons and without my medical
care being affected. I also give permission for information in my
medical records to be used for this project. In any event of publication
and sharing of the data with other researchers and individuals, I
understand that this information will not bear my name or other
identifiers and that due care will be taken to preserve the
confidentiality of this information.

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ {[}Signature/Thumbprint (Right
/ Left) of patient{]}

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (Date of signing)

\begin{quote}
Part II- to be filled by parent / legal guardian, where applicable
\end{quote}

I, \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ hereby give consent for the
above patient to participate in the proposed project. The nature, risks
and benefits of the study have been explained clearly to me and I fully
understand them.

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ {[}Signature/Thumbprint (Right
/ Left) of parent /legal guardian{]}

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (Date of signing)

\begin{quote}
Part III- to be filled witness, where applicable
\end{quote}

An impartial witness should be present during the entire informed
consent discussion if a subject or the subject's legally acceptable
representative is unable to read. After the written informed consent
form and any written information to be provided to subjects, is read and
explained to the subject or the subject's legally acceptable
representative, and after the subject or the subject's legally
representative has orally consented to the subject's participation in
the study and, if capable of doing so, has signed and personally dated
the consent form, the witness should sign and personally date the
consent form.

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (Name of witness)

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (Designation of witness)

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (Signature of witness)

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ (Date of signing)
